%

\documentclass[letterpaper,11pt]{article}

%-----------------------------------------------------------
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage[pdftex]{hyperref}
\hypersetup{
    colorlinks,%
    citecolor=black,%
    filecolor=black,%
    linkcolor=black,%
    urlcolor=mygreylink     % can put red here to visualize the links
}
\urlstyle{same}
\definecolor{mygrey}{gray}{.85}
\definecolor{mygreylink}{gray}{.30}
\textheight=9.0in
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{0.375in}
\addtolength{\textwidth}{0.5in}
\addtolength{\topmargin}{-.375in}
\addtolength{\textheight}{0.75in}

%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\newcommand{\resheading}[1]{{\large \colorbox{mygrey}{\begin{minipage}{\textwidth}{\textbf{#1 \vphantom{p\^{E}}}}\end{minipage}}}}
\newcommand{\ressubheading}[4]{
\begin{tabular*}{6.5in}{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{#3} & \textit{#4} \\
\end{tabular*}\vspace{-6pt}}
%-----------------------------------------------------------

%-----------------------------------------------------------
%General Resume Tips
%   No periods!  Technically, nothing in this document is a full sentence.
%   Use parallelism by ending key words with the same thing,  i.e. "Coordinated; Designed; Communicated".
%   More tips on bottom of this LaTeX document.
%-----------------------------------------------------------

\begin{document}

\newcommand{\mywebheader}{
\begin{tabular*}{7in}{l@{\extracolsep{\fill}}r}
	\textbf{{\LARGE Drew Boardman}} & \href{mailto:drew.e.boardman@gmail.com}{drew.e.boardman@gmail.com}\\
	{\footnotesize {Chicago, IL 60601}} & {(772)-413-8043} \\
	\end{tabular*}
\\
\vspace{0.1in}}

% CHANGE HEADER SOURCE HERE
\mywebheader

%%%%%%%%%%%%%%%%%%%%%%

\resheading{Education}
\begin{itemize}
\item
\ressubheading{\href{http://www.gatech.edu}{Georgia Institute of Technology}}{Atlanta, GA}{\href{http://www.catalog.gatech.edu/colleges/cos/physics/ugrad/phy/geninfo.php}{Bachelor of Science in Physics}}{Aug. 2006 -- May. 2010}
\end{itemize} % End Education list

%%%%%%%%%%%%%%%%%%%%%%
\resheading{Experience}
\begin{itemize}
\item
  \ressubheading{\href{http://www.rallyhealth.com/}{Rally Health}}{Chicago, IL}{Senior Full-Stack Engineer}{Oct. 2019 -- Current}
    { \footnotesize
    \begin{itemize}
        \resitem{Scala}
        \resitem{ElasticSearch, Play, Cats}
        \resitem{Dev Ops: Docker, Jenkins}
        \resitem{Founder/Organizer of Haskell Club}
    \end{itemize}
    }
\item
  \ressubheading{\href{http://www.codemettle.com/}{Codemettle}}{Atlanta, GA}{Software Engineer (Mid)}{Dec. 2017 -- Sept. 2018}
    { \footnotesize
    \begin{itemize}
        \resitem{Scala, ScalaJS, ScalaJS-React}
        \resitem{SOLR, ActiveMQ}
        \resitem{Dev Ops: Docker, GitlabCI}
    \end{itemize}
    }
\item
  \ressubheading{\href{http://www.manheim.com/}{Manheim}}{Atlanta, GA}{Software Engineer (Mid)}{Feb. 2015 -- Dec. 2017}
    { \footnotesize
    \begin{itemize}
        \resitem{Scala: Akka HTTP, ElasticSearch, some Gatling, strong focus on FP}
        \resitem{Ruby: Rails, Sinatra. Capybara, RSpec for testing.}
        \resitem{Javascript: Angular 2, Angular 1 (legacy), some CoffeeScript}
        \resitem{Dev Ops: AWS, Docker, Jenkins for automated deploys (Groovy job DSL/BuildflowDSL)}
        \resitem{Tooling: ArchLinux, VIM}
    \end{itemize}
    }
\item
\ressubheading{\href{http://www.clockwise.md/}{Clockwise.md}}{Atlanta, GA}{Developer Intern}{Nov. 2014 -- Feb. 2015}
    { \footnotesize
    \begin{itemize}
        \resitem{Assist development on Rails 4/Sinatra startup}
        \resitem{Capybara, RSpec}
        \resitem{Work with small team of developers using agile practices}
    \end{itemize}
    }
\item
  \ressubheading{\href{http://www.stratexpartners.com/}{StratEx Partners}}{Chicago, IL}{Implementation Specialist}{Feb. 2013 -- Oct. 2013}
    { \footnotesize
    \begin{itemize}
        \resitem{Lead the Electronic Data Interchange (EDI) team}
        \resitem{Processed all weekly insurance EDI files across a variety of interchange standards}
        \resitem{Focused on the starting-phase implementation of new clients}
        \resitem{Reviewed financial and tax information for clients and all client employees}
        \resitem{Collaborated 1-on-1 with client liaisons to ensure congruence with previous HR systems}
    \end{itemize}
    }

  \item
    \ressubheading{\href{http://phweb.physics.gatech.edu/research/jiang/members.html}{Georgia Institute of Technology}}{Atlanta, GA}{Dr. Zhigang Jiang - Research Assistant}{Feb. 2009 -- May 2010}
    { \footnotesize
    \begin{itemize}
        \resitem{Specialized in the study of Fourier Transform Infrared Spectroscopy of exfoliated graphene}
        \resitem{Assisted in thermal transport and charge carrier mobility measurements of graphene}
        \resitem{Created samples using exfoliation and chemical vapor deposition (CVD) techniques}
        \resitem{Expert in determining sample thickness using Micro-Raman spectroscopy}
        \resitem{Lead research project probing the effect of sub-wavelength apertures and their uses in light amplification}
    \end{itemize}
    }
  \item
    \ressubheading{\href{http://www.magnet.fsu.edu/}{National High Magnetic Field Laboratory}}{Tallahassee, FL}{Certified User}{June 2009 - May 2010}
    { \footnotesize
    \begin{itemize}
        \resitem{Explored the effectiveness of SiO$_{2}$ concentrations in graphene substrates}
        \resitem{Acquired proficiency in cryogenics and their role in superconducting magnets}
        \resitem{Worked within groups of industry leaders and distinguished professors}
    \end{itemize}
    }
\end{itemize}
\end{document}
