\documentclass[letterpaper,11pt]{article}

%-----------------------------------------------------------
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage[pdftex]{hyperref}
\hypersetup{
    colorlinks,%
    citecolor=black,%
    filecolor=black,%
    linkcolor=black,%
    urlcolor=mygreylink     % can put red here to visualize the links
}
\urlstyle{same}
\definecolor{mygrey}{gray}{.85}
\definecolor{mygreylink}{gray}{.30}
\textheight=9.0in
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{0.375in}
\addtolength{\textwidth}{0.5in}
\addtolength{\topmargin}{-.375in}
\addtolength{\textheight}{0.75in}

%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\newcommand{\resheading}[1]{{\large \colorbox{mygrey}{\begin{minipage}{\textwidth}{\textbf{#1 \vphantom{p\^{E}}}}\end{minipage}}}}
\newcommand{\ressubheading}[4]{
\begin{tabular*}{6.5in}{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{#3} & \textit{#4} \\
\end{tabular*}\vspace{-6pt}}
%-----------------------------------------------------------

\begin{document}

\newcommand{\mywebheader}{
\begin{tabular*}{7in}{l@{\extracolsep{\fill}}r}
	\textbf{{\LARGE Drew Boardman}} & \href{mailto:drew.e.boardman@gmail.com}{drew.e.boardman@gmail.com}\\
	{\footnotesize {Greater Orlando Area}} & {(772)-413-8043} \\
\end{tabular*}
\\
\vspace{0.1in}}

% CHANGE HEADER SOURCE HERE
\mywebheader

%%%%%%%%%%%%%%%%%%%%%%
\resheading{Education}
\begin{itemize}
\item
\ressubheading{\href{http://www.gatech.edu}{Georgia Institute of Technology}}{Atlanta, GA}{\href{http://www.catalog.gatech.edu/colleges/cos/physics/ugrad/phy/geninfo.php}{Bachelor of Science in Physics}}{Aug. 2006 -- May. 2010}
\end{itemize} % End Education list

%%%%%%%%%%%%%%%%%%%%%%
\resheading{Experience}
\begin{itemize}
\item
\ressubheading{Rewards Network}{Greater Orlando Area (remote)}{Principal Engineer}{Aug. 2023 -- Current}
    { \footnotesize
    \begin{itemize}
        \resitem{Tech: Scala 3, cats-effect, fs2, fs2-kafka}
        \resitem{Senior contributor to merchants project, a system responsible for onboarding and maintaining merchants and their associated contracts.}
        \resitem{Built several micro-services projects, including some that moved critical business logic from a legacy AS400 to a modern Scala application suite.}
        \resitem{Mentor and provide advice on current FP practices in Scala.}
        \resitem{Collaborated with Data Science team to improve financial models for approving cash products for merchants.}
        \resitem{Utilized Jupyter Notebook, numpy, and sklearn to analyze merchants' financial data and projected risk.}
    \end{itemize}
    }
\item
\ressubheading{Rewards Network}{Chicago, IL}{Senior Engineer}{Dec. 2020 -- Aug. 2023}
    { \footnotesize
    \begin{itemize}
        \resitem{Tech: Scala 3, cats-effect, fs2, fs2-kafka}
        \resitem{Senior contributor to merchants project, a system responsible for onboarding and maintaining merchants and their associated contracts.}
        \resitem{Built several micro-services projects, including some that moved critical business logic from a legacy AS400 to a modern Scala application suite.}
        \resitem{Mentor and provide advice on current FP practices in Scala.}
    \end{itemize}
    }
\item
 \ressubheading{\href{http://www.modaoperandi.com/}{Moda Operandi}}{Chicago, IL}{Senior Engineer}{Sept. 2019 -- Current}
   { \footnotesize
   \begin{itemize}
        \resitem{Tech: Scala, http4s, fs2, circe, cats, Docker, AWS}
        \resitem{Focus on writing pure, non side-effecting applications and libraries.}
        \resitem{Breaking apart Ruby on Rails monolith with event-driven Scala microservices.}
        \resitem{Worked with China orders team. Backed by Kinesis streams and fs2, built distributed Scala
        microservices to handle international orders.}
        \resitem{Most active individual contributor to rebuilding inventory
        service. Also backed by Kinesis and fs2, this project has the goal to
        create single source of truth for inventory. Some challenges include
        each warehouse having different APIs, some of which are nightly SFTP
        drops.  Additionally, moving from having no persistent inventory data
        to keeping real-time up to date inventory.}
    \end{itemize}
    }
\item
  \ressubheading{\href{http://www.rallyhealth.com/}{Rally Health}}{Chicago, IL}{Senior Full-Stack Engineer}{Oct. 2018 -- Sept. 2019}
    { \footnotesize
    \begin{itemize}
        \resitem{Tech: Scala, Play, Cats, ElasticSearch, Docker, Jenkins}
        \resitem{Worked on Cost team to interface with multiple insurance carriers, at the time was the largest profit initiative at the company}
        \resitem{Helped lead rebuilding of the cost-calculation engine. The focus of this project was to take the company from largely 
        facilitating a single insurance carrier to generalize among an ever growing group of new carriers, each with their own response models
        and laws}
        \resitem{Replaced impure legacy codebase to leverage more modern effect systems (cats, cats-effect)}
        \resitem{Frequent lunch-n-learn speaker, Founder/Organizer of Haskell Club}
    \end{itemize}
    }
\item
  \ressubheading{\href{http://www.codemettle.com/}{Codemettle}}{Atlanta, GA}{Software Engineer (Mid)}{Dec. 2017 -- Sept. 2018}
    { \footnotesize
    \begin{itemize}
        \resitem{Tech: Scala, ScalaJS, ScalaJS-React, SOLR, ActiveMQ, Docker, GitlabCI}
        \resitem{Worked on isomorphic Scala application for configuring satellite hardware via a web application.}
        \resitem{Core contributor to sherpa evolved server-side team. Received client data through websockets, and used akka-streams
        and akkaFSM to handle connections with satellite hardware.}
        \resitem{Collaborated with sherpa-evolved front end team. The initiative of this project was to move from a legacy flash-based front end,
        to ScalaJS-React.}
        \resitem{Implemented CI, which was non-existent at the company before.}
    \end{itemize}
    }
\item
  \ressubheading{\href{http://www.manheim.com/}{Manheim}}{Atlanta, GA}{Software Engineer (Mid)}{Feb. 2015 -- Dec. 2017}
    { \footnotesize
    \begin{itemize}
        \resitem{Scala: Akka HTTP, ElasticSearch, some Gatling, strong focus on FP}
        \resitem{Ruby: Rails, Sinatra. Capybara, RSpec for testing.}
        \resitem{Javascript: Angular 2, Angular 1 (legacy), some CoffeeScript}
        \resitem{Dev Ops: AWS, Docker, Jenkins for automated deploys (Groovy job DSL/BuildflowDSL)}
        \resitem{Worked on SellerDashboard team, an application built for facilitating real-time auctions.
        A self-contained team, where each developer was responsible for the
        entire stack, including CI and deployment.}
        \resitem{Built inventory application, the company's first Scala
        service. Solved the problem of sellable inventory and its
        location/quality being unknown before a sale.}
    \end{itemize}
    }
\item
\ressubheading{\href{http://www.clockwise.md/}{Clockwise.md}}{Atlanta, GA}{Developer Intern}{Nov. 2014 -- Feb. 2015}
    { \footnotesize
    \begin{itemize}
        \resitem{Assist development on Rails 4/Sinatra startup}
        \resitem{Capybara, RSpec}
        \resitem{Work with small team of developers using agile practices}
    \end{itemize}
    }
\item
  \ressubheading{\href{http://www.stratexpartners.com/}{StratEx Partners}}{Chicago, IL}{Implementation Specialist}{Feb. 2013 -- Oct. 2013}
    { \footnotesize
    \begin{itemize}
        \resitem{Lead the Electronic Data Interchange (EDI) team}
        \resitem{Processed all weekly insurance EDI files across a variety of interchange standards}
        \resitem{Focused on the starting-phase implementation of new clients}
        \resitem{Reviewed financial and tax information for clients and all client employees}
        \resitem{Collaborated 1-on-1 with client liaisons to ensure congruence with previous HR systems}
    \end{itemize}
    }

  \item
    \ressubheading{\href{http://phweb.physics.gatech.edu/research/jiang/members.html}{Georgia Institute of Technology}}{Atlanta, GA}{Dr. Zhigang Jiang - Research Assistant}{Feb. 2009 -- May 2010}
    { \footnotesize
    \begin{itemize}
        \resitem{Specialized in the study of Fourier Transform Infrared Spectroscopy of exfoliated graphene}
        \resitem{Assisted in thermal transport and charge carrier mobility measurements of graphene}
        \resitem{Created samples using exfoliation and chemical vapor deposition (CVD) techniques}
        \resitem{Expert in determining sample thickness using Micro-Raman spectroscopy}
        \resitem{Lead research project probing the effect of sub-wavelength apertures and their uses in light amplification}
    \end{itemize}
    }
  \item
    \ressubheading{\href{http://www.magnet.fsu.edu/}{National High Magnetic Field Laboratory}}{Tallahassee, FL}{Certified User}{June 2009 - May 2010}
    { \footnotesize
    \begin{itemize}
        \resitem{Explored the effectiveness of SiO$_{2}$ concentrations in graphene substrates}
        \resitem{Acquired proficiency in cryogenics and their role in superconducting magnets}
        \resitem{Worked within groups of industry leaders and distinguished professors}
    \end{itemize}
    }
\end{itemize}
\end{document}
